\documentclass{article}

% package
\usepackage[margin=.5in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}

% detailes
\author{koku17}
\title{Computer Networks Lab}

% presets
\hypersetup{
	hidelinks
}
\pagecolor{black}
\color{white}
\usemintedstyle{one-dark}

% variables
\newcounter{program}

% macros
\newcommand{\question}[1]{
	{
		\centering
		\stepcounter{program}
		\section*{Program \arabic{program}}
	}
	\ifnum \value{program}>1 \vspace{-.8em} \fi
	\addcontentsline{toc}{section}{Program \arabic{program}}
	\item #1
}
\newcommand{\Out}[1]{
	{\centering \section*{Output}}
	\addcontentsline{toc}{subsection}{Output}
	\item[] #1
}
\newcommand{\answer}{\item [$\rightarrow$]}

\begin{document}
	\pagenumbering{gobble} \maketitle \newpage
	\pagenumbering{roman} \tableofcontents \newpage
	\pagenumbering{arabic}
	\begin{enumerate}[label=\arabic*. ]
		\question{
			Implement three nodes point -- to -- point network with duplex links between them. \\
			Set the queue size, vary the bandwidth, and find the number of packets dropped.
		}
		\answer \inputminted{tcl}{../Lab1.tcl} \newpage
		\newpage

		\question{
			Implement transmission of ping messages / trace route over a network topology consisting of 6 nodes.
			\\ Find the number of packets dropped due to congestion.
		}
		\answer \inputminted{tcl}{../Lab2.tcl}
		\newpage

		\question{
			Implement an Ethernet LAN using $n$ nodes and set multiple traffic nodes and plot congestion window
			for different source / destination.
		}
		\answer \inputminted{tcl}{../Lab3.tcl}
		\newpage

		\question{Develop a program for error detecting code using CRC-CCITT (16-bits).}
		\answer \inputminted{tcl}{../CRC.java}
		\newpage

		\question{Develop a program to implement a sliding window protocol in the data link layer.}
		\answer \inputminted{tcl}{../Lab1.tcl}
		\newpage

		\question{
			Develop a program to find the shortest path between vertices using the Bellman-Ford and path vector
			routing algorithm.
		}
		\answer \inputminted{tcl}{../Lab1.tcl}
		\newpage

		\question{
			Using TCP/IP sockets, write a client -- server program to make the client send the file name and to
			make the server send back the contents of the requested file if present.
		}
		\answer \inputminted{tcl}{../Lab1.tcl}
		\newpage

		\question{
			Develop a program on a datagram socket for client / server to display the messages on client side,
			typed at the server side.
		}
		\answer \inputminted{tcl}{../UdpClient.java}
		\newpage

		\question{Develop a program for a simple RSA algorithm to encrypt and decrypt the data.}
		\answer \inputminted{tcl}{../RSA.java}
		\newpage

		\question{Develop a program for congestion control using a leaky bucket algorithm.}
		\answer \inputminted{tcl}{../LeakyBucket.java}
		\newpage
	\end{enumerate}
\end{document}
