\documentclass{article}

%!TEX program=xelatex

% packages
\usepackage[margin=.5in]{geometry}
\usepackage{minted}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

% detailes
\author{koku17}
\title{DBMS Lab Programs}
\date{}

% presets
\urlstyle{same}
\hypersetup{
	colorlinks=true,
	linkcolor=white
}
\pagestyle{empty}
\pagecolor{black}
\color{white}
\usemintedstyle{one-dark}

% macros
\newcommand{\answer}{\item[$\rightarrow$]}

\begin{document}
	\maketitle \newpage
	\begin{enumerate}[label=\arabic*. ]
		\item Create a table called Employee \& execute the following \\
			\texttt{Employee(EMPNO,ENAME,JOB,MANAGER\_NO,SAL,COMMISSION)}
		\begin{enumerate}[label=\roman*) ]
			\item Create a user and grant all permissions to theuser.
			\item Insert the any three records in the employee table contains attributes \\
				\texttt{EMPNO,ENAME JOB,MANAGER\_NO,SAL,COMMISSION} and use rollback and
				Check the result.
			\item Add primary key constraint and not null constraint to the employee table.
			\item Insert null values to the employee table and verify the result
		\end{enumerate}
		\answer \inputminted{mysql}{../Lab1.sql} \newpage
		\item Create a table called Employee that contain attributes
			\texttt{EMPNO,ENAME,JOB,MGR,SAL} \& execute the following
		\begin{enumerate}[label=\alph*) ]
			\item Add a column commission with domain to the Employeetable.
			\item Insert any five records into the table.
			\item Update the column details of job
			\item Rename the column of Employ table using alter command.
			\item Delete the employee whose Empno is 105.
		\end{enumerate}
		\answer \inputminted{mysql}{../Lab2.sql} \newpage
		\item Queries using aggregate functions(COUNT,AVG,MIN,MAX,SUM), Group by, Orderby
			\texttt{Employee(E\_id,E\_name,Age,Salary)}
		\begin{enumerate}[label=\alph*) ]
			\item Add a column commission with domain to the Employeetable.
			\item Create Employee table containing all Records \texttt{E\_id,E\_name,Age,Salary}.
			\item Count number of employee names from employeetable
			\item Find the Maximum age from employee table.
			\item Find the Minimum age from employeetable.
			\item Find salaries of employee in Ascending Order.
			\item Find grouped salaries of employees.
		\end{enumerate}
		\answer \inputminted{mysql}{../Lab3.sql} \newpage
		\item Create a row level trigger for the customers table that would fire for INSERT or UPDAT or
			DELETE operations performed on the CUSTOMERS table. This trigger will display the salary
		difference between the old \& new Salary. \texttt{CUSTOMERS(ID,NAME,AGE,ADDRESS,SALARY)}
		\answer \inputminted{mysql}{../Lab4.sql} \newpage
		\item Create cursor for Employee table \& extract the values from the table.
			Declare the variables, Open the cursor \& extrct the values from the cursor.
			Close the cursor. \\ \texttt{Employee(E\_id,E\_name,Age,Salary)}
		\answer \inputminted{mysql}{../Lab5.sql} \newpage
		\item Write a PL/SQL block of code using parameterized Cursor, that will merge the data available in
			the newly created table \texttt{N\_RollCall} with the data available in the table
			\texttt{O\_RollCall}. \\
			If the data in the first table already exist in the second table then that data should be skipped
		\answer \inputminted{mysql}{Lab6.sql}
	\end{enumerate}
\end{document}
