\documentclass{article}

% package
\usepackage[margin=.5in]{geometry}
\usepackage{calc}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{newtx}

% details
\author{koku17}
\title{Flutter Lab Programs}

% ricing
\def \darkmode{1}
\if1\darkmode
	\pagecolor{black}
	\color{white}
\fi

% presets
\hypersetup{hidelinks}
\pagenumbering{gobble}
\setminted{
	breaklines,
	style=one-dark,
	tabsize=2
}

% macro
\def \answer{\item [$\rightarrow$]}
\newcounter{xcounter}
\def \question#1{
	\item \phantomsection #1
	\stepcounter{xcounter}
	\addcontentsline{toc}{section}{\arabic{xcounter}. #1}
}

\begin{document}
	\pdfbookmark[1]{Title}{T} \maketitle
	\newpage \pagenumbering{roman}
	\pdfbookmark[1]{Contents}{C} \tableofcontents
	\newpage \pagenumbering{gobble}

	\begin{enumerate}
		\question{%
			Develop an application using Flutter to print ``Hello world and
			Hello Flutter".
		}
		\answer \inputminted{dart}{../lab1.dart} \newpage

		\question{%
			Develop an application using Flutter to Increment and Decrement
			Numbers (Counter App).
		}
		\answer \inputminted{dart}{../lab2.dart} \newpage

		\question{Develop Login Screen Application.}
		\answer \inputminted{dart}{../lab3.dart} \newpage

		\pdfpageheight=90.5em
		\textheight=90em \vsize\textheight
		\question{Develop a ``To-do List" Application.}
		\answer \inputminted{dart}{../lab4.dart} \restoregeometry

		\pdfpageheight=114.5em
		\textheight=112em \vsize\textheight
		\question{Develop Calculator Application.} \stepcounter{enumi}
		\answer \inputminted{dart}{../lab5.dart} \restoregeometry

		\pdfpageheight=113.5em
		\textheight=111em \vsize\textheight
		\question{Develop a ``Stopwatch" application using Flutter.}
		\answer \inputminted{dart}{../lab7.dart} \restoregeometry

		\pdfpageheight=297mm
		\question{%
			Develop an application that Navigate from one Screen to another
			(Seamless navigation).
		} \stepcounter{enumi}
		\answer \inputminted{dart}{../lab8.dart} \restoregeometry

		\pdfpageheight=95.5em
		\textheight=93em \vsize\textheight
		\question{Develop an application to implement Animates Logo.}
		\answer \inputminted{dart}{../lab10.dart} \restoregeometry

		\pdfpageheight=100em
		\textheight=95em \vsize\textheight
		\question{%
			Develop an application that tracks our daily Expenses and get a
			report chart.
		}
		\answer \inputminted{dart}{../lab11.dart} \restoregeometry
		\vspace*{\fill}
		\centering \emph{This page left blank intentionally}
		\vspace*{\fill}
	\end{enumerate}
\end{document}
